Development of restored dike grasslands to reference needs more than four years and can hardly modified by local site conditions

### 2023-01-26 manuscript.Rmd
Update manuscript.Rmd

The ordination visualizes the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:figure-nmds)). The NMDS confirms that the seed mixtures are variable, but distinctive for hay meadows and dry grasslands. In addition, it visualizes the decreasing recovery rate on the NMDS1 axis which was already presented (Figure \@ref(fig:figure-recovery)) but the right direction of the development. One exception is that the development of intended hay meadows on the south exposition does not develop towards its seed mixture compositions. The ordination presents the experimental plots not only in context with seed mixtures, but also with reference sites. The reference sites have a bigger variation than the seed mixtures and are close to the seed mixtures but hardly overlap. The positions of reference sites is shifted to the left on the NMDS1 axis which means in the direction of early successional states. On the south exposition, we had negative reference sites which are located in the NMDS in between the positive reference sites and the recent state of restored plots. However, most of negative reference sites (ruderal, dry and anthropogenic vegetation) are situated in the upper half and explicitly recent restoration sites on the south exposition are close to them.

@@

```{r figure-map, fig.cap = "Map", fig.asp = 0.7272}
knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
```

@@

```{r figure-effects, fig.cap = "Effects", fig.asp = 3.3}
knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
```

@@

```{r figure-persistence, fig.cap = "Persistence", fig.asp = 1.785}
knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-fcs, fig.cap = "Favourable Conservation Status (FCS)", fig.asp = 1.785}
knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-recovery, fig.cap = "Recovery", fig.asp = 1.785}
knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-nmds, fig.cap = "NMDS", fig.asp = 1.0312}
knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
```

>>>>

The ordination visualizes the species composition of seed mixtures and the development of the plots over time (Figure \@ref(fig:figure-nmds)). The NMDS confirms that the seed mixtures are variable, but distinctive for hay meadows and dry grasslands. In addition, it visualizes the decreasing recovery rate on the NMDS1 axis which was already presented (Figure \@ref(fig:figure-recovery)) but the right direction of the development. One exception is that the development of intended hay meadows on the south exposition does not develop towards its seed mixture compositions. The ordination presents the experimental plots not only in context with seed mixtures, but also with reference sites. The reference sites have a bigger variation than the seed mixtures and are close to the seed mixtures but hardly overlap. The positions of reference sites are shifted to the left on the NMDS1 axis which means in the direction of early successional states. On the south exposition, we had negative reference sites which are located in the NMDS in between the positive reference sites and the recent state of restored plots. However, most of negative reference sites (ruderal, dry and anthropogenic vegetation) are situated in the upper half and explicitly recent restoration sites on the south exposition are close to them.

@@

```{r figure-map, fig.cap = "Map", fig.asp = 1.2854, fig.width = 5}
knitr::include_graphics(here::here("outputs", "figures", "figure_1_map.png"))
```

@@

```{r fig.id = "figure-effects", fig.cap = "Effects", fig.asp = 0.3030, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
```

@@

```{r fig.id = "figure-persistence", fig.cap = "Persistence", fig.asp = 0.4848, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x8cm.tiff"))
```

@@

```{r fig.id = "figure-fcs", fig.cap = "Favourable Conservation Status (FCS)", fig.asp = 0.4848, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x8cm.tiff"))
```

@@

```{r fig.id = "figure-recovery", fig.cap = "Recovery", fig.asp = 0.4848, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x8cm.tiff"))
```

@@

```{r fig.id = "figure-nmds", fig.cap = "NMDS", fig.asp = 0.9696, fig.width = 6.49}
knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
```
